Infinite products and zero--one laws in categorical probability

### 2020-06-19 categorical-zero-one.tex
Fixed refs
There was an issue with the Giry ref somewhere, although I'm honestly
not sure what. Seems fixed now.
Also fixed abbrev. of the danish journal, as per Dusko's suggestion
Added Cartesian cats as example

	As a first application, we state and prove versions of the zero--laws of Kolmogorov and Hewitt--Savage laws for Markov categories. This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts. % For example, applying the Kolmogorov zero--one law to the Kleisli category of the hyperspace monad on topological spaces gives a criterion for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.

@@

@@

\begin{definition}[{\cite[Definition~10.1]{markov_cats}}]
	Let $\cC$ be a Markov category. A morphism $f : X \to Y$ in $\cC$ is \emph{deterministic} if it is a comonoid homomorphism,
	\[
		\tikzfig{multiplication_natural}	
	\]
\end{definition}

>>>>

	As a first application, we state and prove versions of the zero--one laws of Kolmogorov and Hewitt--Savage for Markov categories. This gives general versions of these results which can be instantiated not only in measure-theoretic probability, where they specialize to the standard ones in the setting of standard Borel spaces, but also in other contexts. % For example, applying the Kolmogorov zero--one law to the Kleisli category of the hyperspace monad on topological spaces gives a criterion for when maps out of an infinite product of topological spaces into a Hausdorff space are constant.

@@

\begin{example}
  Any Cartesian monoidal category is obviously semicartesian. In the probabilistic setting that we are considering, this corresponds to a situation in which there is no randomness
  (in such a category, all morphisms are deterministic, cf. \cref{determ_def}). Hence it is somewhat uninteresting from our point of view.
\end{example}

@@

\begin{definition}[{\cite[Definition~10.1]{markov_cats}}]\label{determ_def}
	Let $\cC$ be a Markov category. A morphism $f : X \to Y$ in $\cC$ is \emph{deterministic} if it is a comonoid homomorphism,
	\[
		\tikzfig{multiplication_natural}	
	\]
\end{definition}
